---
title: 'Reproducible research using markdown documentation'
author: "Jens Roeser"
output: 
  ioslides_presentation:
    incremental: false
    transition: slower
    widescreen: true
    css: slides.css
bibliography      : ["../refs/references.bib"]
---

<style>
.forceBreak { -webkit-column-break-after: always; break-after: column; }

slides > slide.backdrop {
  background: white;
}

div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 15px;
  width: 80%;
  font-size: 0.6em;
}

pre {
  font-size: 15px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, message = FALSE, comment=NA)
options("kableExtra.html.bsTable" = T, digits = 2)
options(pillar.print_min = 5, pillar.print_max = 6)
library(tidyverse)
library(knitr)
library(kableExtra)
```

## R markdown

- combination of text, (R)code, and data
- documentation of all analysis steps (for us and our readers)
- quickly updating and repeating analysis
- communication of analysis / results 
- producing texts, website, supplementary materials, walkthroughs, APA style manuscripts, slides
- easy cross referencing of tables and figures, citations 
- automatically compiling reference lists
- compiles into `.pdf`, `.html`, `.docx`, `.doc`
- some knowledge of LaTeX useful for cross-referencing, using additional features (LaTeX add-ons), writing equations 

## Setup

```{r eval = FALSE}
install.packages("rmdformats")
```

or 

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("juba/rmdformats")
```

## From the R-Studio menu ...

- `File` > `New File` > `R Markdown`
- Document (PDF, WORD, HTML)
- from template: 
  - e.g. `readthedown` or `robobook` for documents
  - `rmdshower::shower_presentations` for slides

## Documents

- example: <https://rpubs.com/jensroes/765467>
- online sharing on RPubs ("Publish")
- create from template:
  - `File` > `New File` > `R Markdown`
  - `robobook`
- we'll develop a `robobook` markdown together with all fundamental features

## APA manuscripts using `papaja`

- example: <https://osf.io/vayhq/> published in @roeser2021modelling
- installation: <https://github.com/crsh/papaja>
  - `File` > `New File` > `R Markdown`
  - "APA article (6th edition)" using `papaja`
- template for APA article (7th edition)

## Task

- Reproduce analysis in `apa7_template.Rmd`
- Redo analysis for either dominant or non-dominant hand or foot: change as little code as possible


## References

```{r eval = F, echo = F}
<style>
slides > slide { overflow: scroll; }
slides > slide:not(.nobackground):after {
  content: '';
}
</style>
```


